Modelling Weddell Sea Food Web

### 2022-06-06 ModellingWeddellSea.Rmd
Update indices

@@

# Read the network file (from the same source but different format)
#
wedd <- readNetwork("Data/Wedd.dat",edgeListFormat = 2)

@@

@@

# Check detritus
#
detritus <- wedd_df %>% filter(grepl("tritus",res_taxonomy)) 
detritus <- wedd_df %>% filter(is.na(interaction_dim))
write_tsv(wedd_df %>% arrange(interaction_dim), "Data/Wedd_mass.dat")

wedd_df <- read_delim("Data/Wedd_mass_complete.dat",delim=" ")

@@

```{r calcunweightedtopo, eval=TRUE,echo=F,message=T,warning=T}

@@

>>>>

* Initially we read this an then we saved it with less fields to add information not present in the database about dimensionality of interactions 2D or 3D

@@

@@

write_tsv(wedd_df %>% arrange(interaction_dim), "Data/Wedd_mass.dat")

@@

# Read the updated database
#
wedd_df <- read_delim("Data/Wedd_mass_complete.dat",delim=" ")

# Check detritus
#
detritus <- wedd_df %>% filter(grepl("tritus",res_taxonomy)) 
detritus <- wedd_df %>% filter(is.na(interaction_dim))

@@

```{r calc_unweighted_metrics, eval=TRUE,echo=F,message=T,warning=T}

@@

```{r calc_weighted_metrics, eval=TRUE,echo=F,message=T,warning=T}

weightedNets <- tibble()

weightedTbl <- tibble()
tp <- calc_weighted_topological_indices(g)
#tp <- bind_cols(tp, calcIncoherence(g1)) 
tp <- bind_cols(tp, calc_QSS(g,10000,48, istrength=TRUE))

# Modularity should be repeatedly calculated because is a stochastic algorithm
#
plan(multisession)
wm <- future_lapply(seq_len(100),function(X){
  wm <- calc_modularity(g,weights = NULL) 
  })
modularityTbl <- bind_rows(wm %>% mutate(type="weighted"))

tp <- bind_cols(tp, summarise(modularityTbl, Modularity=mean(Modularity)))

weightedTbl <- bind_rows(weightedTbl, tp)                 ## Modularity -49643343 what happens if all the weights have the average weigth valus?????????

lred <- curveBall(g,1000,istrength=TRUE)
tp <- calc_weighted_topological_indices(lred,ncores=48)
tp <- bind_cols(tp, calc_modularity(lred,ncores=48,weights = NULL))

# tp0 <- calcModularitySWnessZScore(g,lred,ncores=48)  -----> Against which model do we calculate SWness in the weighed case???????????
# tp1 <- tp0$da %>% dplyr::select(Modularity:isSWness)
# websTbl <- bind_cols(websTbl,tp1)

weightedNets <- tp 
rm(tp,tp0,lred,tp1)
save.image()
